msre reactor design

### 2022-06-24 core/docs/msrecore.tex
typo

\textcite[page 1]{ornl-tm-3229} states about the flow through the reactor:
\enquote{\textit{the fuel enters the reactor vessel at 1200 gpm through a constant flow area volute near the top of the cylindrical section. because of the vaiable pressure gradient in a volute of this type, orifices are used to obtain a uniform angular flow distribution to the core wall cooling annulus. the fuel then swirls down the core wall cooling annulus and into the reactor vessel lower head. radial vanes are placed in the lower head to destroy the swirl generated by the volute. the lower head then serves as a plenum to direct the fuel uniformly to the moderator region. the moderator region is composed of log graphite core blocks, square in cross section, and with grooves cut longitudinally in the 4 faces. when these stringers are assembled vertically together, the grooves form the fuel passages... after passing through the moderator, the fuel then goes into the vessel upper head which serves as a collection plenum and directs the fuel to the outlet pipe.}}

>>>>

\textcite[page 1]{ornl-tm-3229} states about the flow through the reactor:
\enquote{\textit{the fuel enters the reactor vessel at 1200 gpm through a constant flow area volute near the top of the cylindrical section. because of the variable pressure gradient in a volute of this type, orifices are used to obtain a uniform angular flow distribution to the core wall cooling annulus. the fuel then swirls down the core wall cooling annulus and into the reactor vessel lower head. radial vanes are placed in the lower head to destroy the swirl generated by the volute. the lower head then serves as a plenum to direct the fuel uniformly to the moderator region. the moderator region is composed of log graphite core blocks, square in cross section, and with grooves cut longitudinally in the 4 faces. when these stringers are assembled vertically together, the grooves form the fuel passages... after passing through the moderator, the fuel then goes into the vessel upper head which serves as a collection plenum and directs the fuel to the outlet pipe.}}
